Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-08-09 ms.tex
added results of dark vs illuminated e-/px comparison test

\subsubsection{Pre-Ampflier Reset Test}
We also explored the difference between resets per frame versus resets per integrations as discussed in Section \ref{sec:preAmp}.
We used a stripe mode 2048x256 with reference pixels on the bottom and sides.

@@

>>>>

\subsubsection{Pre-Amplifier Reset Test}
We also explored the difference between resets per frame versus resets per integrations as discussed in Section \ref{sec:preAmp}.
We used a stripe mode 2048x256 with reference pixels on the bottom and sides.

@@

We also repeat the long baseline test with a 2048x256 subarray and 8 groups up the ramp but this time with no illumination.
This allows us to compare the noise in e-/px when illuminated versus the noise in e-/px.
If these two values are the same, this indicates that electronic noise enters both detectors and limits photometry precision in ppm.
We find instead that the illuminated data has a much higher standard deviation (9 e$^-$/px, compared to the theoretical 1.8 e$^-$/px averaged over the aperture).
The dark time series had a standard deviation of 1.9 e$^-$/px compared to the theoretical (uncorrelated) 0.2 e$^-$/px averaged over the aperture.
